Measurement Bias from Address Aliasing

### 2016-05-25 presentation.tex
Reorder slides
Improve stuff

\usetikzlibrary{patterns,shapes,positioning,calc}
\setbeamertemplate{bibliography item}[text]
\lstset{language=C, basicstyle=\ttfamily\scriptsize, columns=flexible, belowskip=0pt}
\newcommand{\perfctr}[1] {
  {\lowercase{#1}}
}

@@

\date[2016] % (optional)
{International Workshop on Automatic Performance Tuning, Chicago, May 2016}

@@

@@

\begin{itemize}
  \item Identify address aliasing as an underlying explanation for measurement bias.
  \item See how aliasing affects dynamic memory allocation.
  \item Look at opportunities to optimize for aliasing.
  \item Up to 2x speedup.
\end{itemize}

@@

\begin{itemize}
  \item Runtime performance change from external factors.
  \begin{itemize}
    \item Environment variables
    \item Link ordering
  \end{itemize}
  \item Challenge for performance analysis.
  \item Effects can invalidate perceived speedup~\cite{Mytkowicz:2008:OE&MB}.
\end{itemize}

@@

\begin{figure}
  \begin{lstlisting}[frame=single, xleftmargin=.01\textwidth, xrightmargin=.01\textwidth, aboveskip=-2pt]
static int i, j, k;

% Also an optimization problem (relevant for auto-tuning).

% Also an optimization problem (relevant for auto-tuning).

\begin{table}
  %\centering
  \caption{Events with significant correlation to cycle count.\label{tab:loopcorrelation}}
  \pgfplotstabletypeset[
    int detect, % Output whole numbers for counter values
    col sep=comma,
    columns={Performance counter, Median, [index]3, [index]4},
    column type=r,
    font=\footnotesize,
    columns/Performance counter/.style={
      string type, 
      column type=l,
      column type/.add={|}{},
      postproc cell content/.append code={
        \pgfkeysalso{@cell content=\perfctr{##1}}
      }
    },
    every head row/.style={
      output empty row,
      before row={\hline
        Performance counter & Median & Spike 1 & Spike 2 \\
      },
      after row=\hline\hline
    },
    every last row/.style={after row=\hline},
    every last column/.style={column type/.add={}{|}}
  ]{bin/microkernel-comparison-haswell.csv}
\end{table}

@@

\begin{figure}[t]
% Convolution example code
  \lstinputlisting[
    language=C,
    frame=single,
    xleftmargin=.00\textwidth,
    xrightmargin=.00\textwidth,
    aboveskip=-5pt
  ]{bin/convolution-kernel.c}
  \caption{Simplified implementation of convolution with a fixed kernel.}
  \label{lst:conv}
\end{figure}

>>>>

\usetikzlibrary{patterns,shapes,positioning,calc}
\setbeamertemplate{bibliography item}[text]
\lstset{language=C, basicstyle=\ttfamily\footnotesize, columns=flexible, belowskip=0pt}
\newcommand{\perfctr}[1] {
  {\lowercase{#1}}
}

@@

\date[2016] % (optional)
{International Workshop on Automatic Performance Tuning, Chicago, May 27. 2016}

@@

What if changing your user name affected the execution time of your programs?
%How changing user name can affect performance of executing programs.

%Results being skewed from \"true\" value due to how measurements are performed.
\vspace{1cm}

\begin{itemize}
  \item Runtime performance change from external factors.
  \begin{itemize}
    \item Environment variables
    \item Link ordering
  \end{itemize}
  \item Challenge for performance analysis. Comparison of algorithms on different system configurations can give misleading results.
  \item Effects can invalidate perceived speedup~\cite{Mytkowicz:2008:OE&MB}.
\end{itemize}

@@

\begin{itemize}
  \item Identify address aliasing as an underlying explanation for measurement bias.
  \item How aliasing affects dynamic memory allocation.
  \item Benchmark results.
  \item Opportunities to optimize for aliasing.
  %\item Up to 2x speedup.
\end{itemize}

@@

\begin{figure}
  \begin{lstlisting}[frame=single, xleftmargin=.01\textwidth, xrightmargin=.01\textwidth]
static int i, j, k;

% Also an optimization problem (relevant for auto-tuning).
\framebreak

@@

\begin{frame}[fragile]
\frametitle{Results}
\begin{table}
  \caption{Events with significant correlation to cycle count.\label{tab:loopcorrelation}}
  \pgfplotstabletypeset[
    int detect, % Output whole numbers for counter values
    col sep=comma,
    columns={Performance counter, Median, [index]3, [index]4},
    column type=r,
    font=\footnotesize,
    columns/Performance counter/.style={
      string type, 
      column type=l,
      column type/.add={|}{},
      postproc cell content/.append code={
        \pgfkeysalso{@cell content=\perfctr{##1}}
      }
    },
    every head row/.style={
      output empty row,
      before row={\hline
        Performance counter & Median & Spike 1 & Spike 2 \\
      },
      after row=\hline\hline
    },
    every last row/.style={after row=\hline},
    every last column/.style={column type/.add={}{|}}
  ]{bin/microkernel-comparison-haswell.csv}
\end{table}
\end{frame}

@@

\begin{figure}[t]
% Convolution example code
  \lstinputlisting[
    language=C,
    frame=single,
    xleftmargin=.00\textwidth,
    xrightmargin=.00\textwidth,
    aboveskip=-5pt,
    basicstyle=\ttfamily\scriptsize
  ]{bin/convolution-kernel.c}
  \caption{Simplified implementation of convolution with a fixed kernel.}
  \label{lst:conv}
\end{figure}
